### 2020-02-09 README.Rmd
finalize() is a reserved word for R6. Must change it to () to prevent future problem.
calculate TLO, fix #4

After the coding, you need to first finalize the test. Then, you can look at the model precision by printing the oolong test.

```{r, eval = FALSE}
oolong_test$finalize()
oolong_test
```

@@

>>>>

After the coding, you need to first lock the test. Then, you can look at the model precision by printing the oolong test.

```{r, eval = FALSE}
oolong_test$lock()
oolong_test
```

@@

Similarly, use the `$do_topic_intrusion_test` to code the test cases, lock the test with `$lock()` and then you can look at the TLO (topic log odds) value by printing the oolong test.

```{r, eval = FALSE}
oolong_test$lock()
oolong_test
```

## References

1. Chang, J., Gerrish, S., Wang, C., Boyd-Graber, J. L., & Blei, D. M. (2009). Reading tea leaves: How humans interpret topic models. In Advances in neural information processing systems (pp. 288-296).
